Exploratory data analysis

### 2023-08-12 index.qmd
add fim por to epc kendall

This plot shows the significant increasing or decreasing temperature trends for all long-term monitoring stations (EPCHC) in Tampa Bay, by period of record and sampling location in the water column. The periods of record are 1974-2022 (whole record), 2007-2022 ([NOAA record](https://coastwatch.noaa.gov/cw_html/cwViewer.html)), 2000-2015 (seagrass recovery), and 2016-2022 (seagrass decline). The latter two periods of record likely have low statistical power with limited sample size. Seasonal Mann-Kendall tests are used.

@@

::: panel-tabset
```{r}
#| results: asis
fls <- list.files(here('figs'), 'segsum_', full.names = F) %>% 
  rev
locs <- fls %>% 
  basename %>% 
  gsub('^segsum_|\\.png', '', .)
for(loc in seq_along(locs)){
  cat('## ', locs[loc], '\n\n')

>>>>

This plot shows the significant increasing or decreasing temperature trends for all long-term monitoring stations (EPCHC) in Tampa Bay, by period of record and sampling location in the water column. The periods of record are 1974-2022 (whole record), 2007-2022 ([NOAA record](https://coastwatch.noaa.gov/cw_html/cwViewer.html)), 1996-2020 (FIM record), 2000-2015 (seagrass recovery), and 2016-2022 (seagrass decline). The latter two periods of record likely have low statistical power with limited sample size. Seasonal Mann-Kendall tests are used.

@@

::: panel-tabset
```{r}
#| results: asis
#| out-width: 80%
fls <- list.files(here('figs'), 'segsum_', full.names = F) %>% 
  rev
locs <- fls %>% 
  basename %>% 
  gsub('^segsum_|\\.png', '', .)
for(loc in seq_along(locs)){
  cat('## ', locs[loc], '\n\n')
